Lineal regression with one variable and one parameter for the cost function

### 2016-07-08 LinearRegression/Documentation/OneParam/OneParam.tex
adding octave implementation all, info with one paramter redy

%

@@

    What you shoul do

    Now lets analyze the formula, the fist simbol is the $\theta$ that is the
    parameter of the cost function, the second is the $:=$ which means assign,
    this make sence because we are trying to update the parameter of the
    function trying to make it as closer to the minimum as possible. Then we
    have a the actual value of $\theta$ followed by a substraction and a
    $\alpha$ simbol, we are goint to talk about this later, now we get to de
    most important part of the formula, the derivative ($\frac{d}{d \theta}$).\\

    the idea is that we are going to start in a point that is located at any
    part of the graphic, it could be far or close to the minimum, remember that
    this point is the result of the cost function for a line, and what we want
    to do is to start updating the value of $\theta$ because is the value that
    makes that the error will be big or small ($J(\theta)$).\\

    \begin{tikzpicture}
        \begin{axis}[
                     xlabel=$\theta$,
                     ylabel=$J(\theta)$,
                     ymin=0, ymax=25,
                     xtick=\empty,
                     ytick=\empty
                    ]
            \addplot[mark=none, color=red]{x^2};

            \draw[thick,->] (axis cs: 4,0) -- node[left]{$\theta_1$} (axis cs: 4,16);

            \addplot[color=blue, only marks]
            coordinates{
                (4,16)
                (2,4)
                (1,1)
                (0,0)
            };
        \end{axis}
    \end{tikzpicture}

    This can be done by calculating the direcction and that we want to follow

@@

    Now the first thing to do in order to use the gradient desent in our cost
    function is replace the function $J(\theta)$ in the formula

>>>>

@@

    Lets see how can we make our way to the bottom of the valley, the first
    thing to do is find a direction, in order to do this we must know the
    inclination of the side where you are, then start going to the lower place.
    Lets assume that you start in the top left point, when you start going down
    the hill, with a constant step size (this is very important for the
    example), you should notice that you have a big advance with each step
    becouse of the high inclination, but when you are aproaching your friends
    the inclunation is lower and you start to get smaller steps until you get
    your friends and stop walking.

    \newpage

    Now that we have seen the example lets analyze the formula, the fist symbol
    is the $\theta$ that in the example is your position but in the
    formula is the parameter of the cost function, the second symbol is $:=$
    which means that we are updating the value or assigning a new one,
    this make sence because we are trying to get closer to our friends which
    means update the cost function ($J(\theta)$) to the minimum. Then we
    have a second $\theta$ that is your actual possition in the example and
    the actual value of $\theta$ in the formula, followed by a substraction
    that means that we are going to decrement the actual value of $\theta$
    and then assign the new value to $\theta$ trying to get the minimum,
    that means update the value, in the example means walk, then we get an
    $\alpha$ symbol which is a positive number, this represent the step size,
    and is a constant, now we get to the most important part of the formula, the
    derivative ($\frac{d}{d \theta}$).

    Remember that the first thing we do in the example was looked at the
    inclunation of the hill where we are, this in order to know if we should
    move right or left. Now, as you may know a derivative is basicaly the
    slope of a function in a point, this is perfect for us because fit our
    request perfectly. Lets imaging that we start at the right side of the
    valley, so we what to go left, now mathematically the derivative of the
    point situated in the right side of the function is positive because the
    slope is pointing the right, so the term $\frac{d}{d \theta}$ will be a
    positive number, that will be multiplied by a factor ($\alpha$) and then
    substracted to the actual value of $\theta$, just as we want.
    Now lets imaging that we end up in the left side of the valley, in that case
    we want to go right, now mathematically the derivative of a point that is
    situated in the left side of the function will be negative because the
    slope is pointing to the left, this means that the term $\frac{d}{d \theta}$
    will be a negative number, that will be multiplied by the factor ($\alpha$)
    and then added to the actual value of $\theta$ (remember that - * - = +),
    fiting perfectly what we want. now a few ilustrations to show better what we
    are talking about.

    \vspace{3cm}

    \begin{figure}[h]
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                         title=Gradient decend movement description,
                         xlabel=$\theta$,
                         ylabel=$J(\theta)$,
                         ymin=-5, ymax=25,
                         xtick=\empty,
                         ytick=\empty
                        ]
                \addplot[mark=none, color=black]{x^2};

                \addplot[color=red, only marks]
                    coordinates{
                        (4,16)
                        (-4,16)
                    };

                \node[above] at (axis cs: 0,1.5) {Minimum};

                \draw[thick,->] (axis cs: 3.5,4) -- node[right]{+} (axis cs: 5.5,20);
                \draw[thick,->] (axis cs: -3.5,4) -- node[left]{-} (axis cs: -5.5,20);

                \draw[thick,->] (axis cs: -6,-4) -- node[above]{Increment $\theta$} (axis cs: -0.1,-4);
                \draw[thick,->] (axis cs: 6,-4) -- node[above]{Increment $\theta$} (axis cs: 0.1,-4);

            \end{axis}
        \end{tikzpicture}
    \end{figure}

@@

    \newpage

    Now to finish the explanation remember the second part of the example, when
    you start to walk, with a constant step size, down the hill you start
    making a big advance because of the inclunation, but when you are getting
    closer to your friends the distance that you move with just one step is
    smaller because the slope of the hill is lower. This is just what we are
    trying to show in the last couple of grafics, notice that when the $\theta$
    is getting closer to the minimum the arrow that represents the movement is
    smaller, this is always going to happen because the inclunation of the hill
    is slower so you move less.\\

    Until the moment what we have done is to show the generic version of the
    gradient desent, what we are goint to do now is to replace the function
    $J(\theta)$ for our cost function and apply the derivative to the formula
    in order to get the gradient desend for our particular case.

    Lets start, the first thing to do in order to use the gradient desent in our
    cost function is replace the function $J(\theta)$ in the formula
